Priors

### 2023-06-25 reports/county_figures.Rmd
add version 7

county <- tar_read(ma_v1, 
                   store =targets_dir) %>% 
  mutate(version = "v1") %>%
  bind_rows(
    tar_read(ma_v2,
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(ma_v3, 
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(ma_v4, 
             store =targets_dir)
  )%>%
   bind_rows(
    tar_read(ma_v5,
             store =targets_dir)
  )%>%
   bind_rows(
    tar_read(ma_v6,
             store =targets_dir)
   )

@@

versions <- tibble(
  version = c("v1", "v2", "v3", "v4", "v5", "v6"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,County\\,and\\,Date$", 
    "$\\beta$ Centered at Emp. Value",
    "$P(S_1|untested)$ Centered at Emp. Value",
    "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)"
    ),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,County\\,and\\,Date$", 
        "$\\beta$ Centered at Emp. Value",
         "$P(S_1|untested)$ Centered at Emp. Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)"

@@

@@

covidestim_correlations <- w_data %>%
  filter(!is.na(infections_std)) %>%
  group_by(vlabel) %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(exp_cases_median_std,infections_std,
                              use = "complete.obs")) %>%
  mutate(x=2.5,
         y=.1)

@@

@@

```{r, fig.width=15}

@@

#########################################################
# CONCORDANCE BY VERSION 
#########################################################
ma_concordance %>%
  left_join(in_interval) %>%
  mutate(in_interval=factor(in_interval, 
                            levels=c("Above Interval",
                                      "In Interval",
                                     "Below Interval"))) %>%
  ggplot(aes(y =fct_reorder(vlabel,n_interval),
             x = prop, 
             fill=in_interval)) +
  #facet_wrap(~fct_reorder((vlabel),m), ncol=1) +
  geom_bar(stat="identity",position="stack", color="darkgray", linewidth=.2) +
#  viridis::scale_fill_viridis(option="mako", begin=.2, discrete=TRUE) +
  theme_c(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1)) +
  theme(
          plot.subtitle = element_text(size=18, face='italic', 
                                       margin=margin(4,0,4,0))) +
  scale_y_discrete(labels=unname(TeX(labels))) +
  labs(y ="",
       x="Proportion",
       fill = "Covidestim Median:",
       title = "Where Covidestim Medians Fall\nRelative to Probabilistic Bias Intervals",
       subtitle = "By Version, in Massachusetts") +
  scale_fill_manual(values=c("Below Interval"="#7997D2",
                             "In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79"),
                     breaks = c("Below Interval",
                               "In Interval",
                               "Above Interval")) +
  guides(fill=guide_legend(byrow=TRUE)) +
  scale_x_continuous(n.breaks = 7,
                     expand=c(0,0),
                     limits=c(-.05,1))

ma_concordance %>%
  group_by(vlabel) %>%
  mutate(total=sum(n_per_version)) %>%
  filter(in_interval == "In Interval") %>%
  mutate(n_interval = n_per_version) %>%
  ggplot(aes(y=fct_reorder(vlabel,prop), x=prop)) +
  geom_text(aes(label=round(prop,3), x= prop+.03), 
             angle=0) +
  geom_bar(stat="identity", fill="#596281") +
  scale_y_discrete(breaks= unique(ma_concordance$vlabel),
                   labels=function(x)TeX(x)) +
  scale_x_continuous(expand=c(0,0), 
                     limits=c(0,.9), n.breaks=7)  +
  theme_c() +
  labs(y="",
       x="Proportion Containing the Covidestim Median",
       title="Proportion Containing the Covidestim Median\nBy Implementation")

@@

>>>>

county <- tar_read(ma_v1, 
                   store =targets_dir) %>% 
  mutate(version = "v1") %>%
  bind_rows(
    tar_read(ma_v2,
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(ma_v3, 
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(ma_v4, 
             store =targets_dir)
  )%>%
   bind_rows(
    tar_read(ma_v5,
             store =targets_dir)
  )%>%
   bind_rows(
    tar_read(ma_v6,
             store =targets_dir)
   )%>%
   bind_rows(
    tar_read(ma_v7,
             store =targets_dir)
   )

@@

versions <- tibble(
  version = c("v1", "v2", "v3", "v4", "v5", "v6", "v7"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "$\\beta$ Centered at Emp. Value",
    "$P(S_1|untested)$ Centered at Emp. Value",
    "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by Date$\\,$"
    ),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
        "$\\beta$ Centered at Emp. Value",
         "$P(S_1|untested)$ Centered at Emp. Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by Date$\\,$"

@@

```{r}
plt_wastewater_pb <- w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  labs(x = "Probabilistic Bias Counts\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "")

@@

covidestim_correlations <- w_data %>%
  filter(!is.na(infections_std)) %>%
  group_by(vlabel) %>%
  # missing values are handled by casewise deletion
  summarize(Correlation = cor(exp_cases_median_std,infections_std,
                              use = "complete.obs")) %>%
  mutate(x=2.8,
         y=.1)

@@

cor_waste %>%
  left_join(cor_covid) %>%
  mutate(vlabel = gsub(
    "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "Priors Do Not Vary by State and Date",
    vlabel, fixed=TRUE),vlabel=gsub(" at","\nat", vlabel)) %>%
  arrange(desc( `Correlation with Wastewater Concentrations`)) %>%
  rename(Implementation = vlabel) %>%
  kbl() %>%
  kable_styling(full_width = TRUE)

@@

```{r, fig.width=13}

@@

#########################################################
# CONCORDANCE BY VERSION 
#########################################################
ma_concordance %>%
  left_join(in_interval) %>%
  mutate(in_interval=factor(in_interval, 
                            levels=c("Above Interval",
                                      "In Interval",
                                     "Below Interval"))) %>%
  ggplot(aes(y =fct_reorder(vlabel,n_interval),
             x = prop, 
             fill=in_interval)) +
  #facet_wrap(~fct_reorder((vlabel),m), ncol=1) +
  geom_bar(stat="identity",position="stack", color="darkgray", linewidth=.2) +
   theme_c(axis.text.y = element_text(size = 14, hjust=1),
          axis.title.x = element_text(size=14),
          axis.text.x=element_text(size=10),
          legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt')) +
  scale_y_discrete(labels=unname(TeX(labels))) +
  labs(y ="",
       x="Proportion Containing the Covidestim Median",
       fill = "Covidestim Median:",
       title = "Where Covidestim Medians Fall\nRelative to Probabilistic Bias Intervals",
       subtitle = "By Implementation, in Massachusetts") +
  scale_fill_manual(values=c("Below Interval"="#7997D2",
                             "In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79"),
                     breaks = c("Below Interval",
                               "In Interval",
                               "Above Interval")) +
  guides(fill=guide_legend(byrow=TRUE)) +
  scale_x_continuous(n.breaks = 7,
                     expand=c(0,0),
                     limits=c(-.05,1))

@@

```{r, fig.width=12.3}

ma_concordance %>%
  group_by(vlabel) %>%
  mutate(total=sum(n_per_version)) %>%
  filter(in_interval == "In Interval") %>%
  mutate(n_interval = n_per_version) %>%
  ggplot(aes(y=fct_reorder(vlabel,prop), x=prop)) +
  geom_text(aes(label=round(prop,3), x= prop+.03), 
             angle=0) +
  geom_bar(stat="identity", fill="#596281") +
  scale_y_discrete(breaks= unique(ma_concordance$vlabel),
                   labels=function(x)TeX(x)) +
  scale_x_continuous(expand=c(0,0), 
                     limits=c(0,.9), n.breaks=7)  +
  theme_c(axis.text.y = element_text(size = 13, hjust=1),
          axis.title.x = element_text(size=14),
          axis.text.x=element_text(size=10)) +
  labs(y="",
       x="Proportion Containing the Covidestim Median",
       title="Proportion Containing the Covidestim Median",
       subtitle = "By Implementation")

# Summary of Comparison Between Implementations

Although the spline-smoothing improved the correlations, it did not improve the proportion containing the Covidestim median.

The implementation centering $\Pr(S_1|\text{untested})$ at the survey value along with the implementation that does not vary the priors by state or date are the most correlated with Covidestim estimates, wastewater concentrations, and  have the highest proportion of county-biweeks containing the Covidestim median.

### 2023-06-25 reports/priors.Rmd
add version 7

```{r,include=FALSE}
ctis %>%
  ggplot(aes(x = beta, fill=state)) +
  geom_density() +
  scale_fill_viridis(option="mako", discrete=TRUE) +
  theme_c() +
  facet_wrap(~state)

@@

>>>>

```{r,include=FALSE}

ctis %>%
  ggplot(aes(x = beta, fill=state)) +
  geom_density() +
  scale_fill_viridis(option="mako", discrete=TRUE) +
  theme_c() +
  facet_wrap(~state)

@@

ctis %>%
  group_by(state) %>%
  summarize(mean=mean(beta,na.rm=TRUE)) %>%
  pull(mean) %>%
  mean()

ctis %>%
  group_by(state) %>%
  summarize(mean=mean(smoothed_wcli,na.rm=TRUE)) %>%
  pull(mean) %>%
  mean()
